SDR enhancement by clouds

### 2024-03-15 GHI_enh_04_investigate.tex
Commit 2024-03-15 12:14
Commit 2024-03-15 13:12

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-14}

@@

lmD: 1.566006 +/- 0.1083205

lmY: 1.566022 +/- 0.1083224

Arima: 1.5664 0.1467 10.6786 0

@@

lmD: 0.9508037 +/- 0.1552487

lmY: 0.9508275 +/- 0.1552514

Arima: 1.0223 0.2369 4.3149 0

@@

lmD: 1.086985 +/- 0.1678711

lmY: 1.087013 +/- 0.1678741

Arima: 1.16 0.2511 4.6198 0

@@

lmD: -0.01234536 +/- 0.1388793

lmY: -0.01233011 +/- 0.1388818

@@

Arima: -0.0132 6.9042 -0.0019 0.9985

@@

Arima: 33.7214 8.8815 3.7968 1e-04

@@

lmD: 0.003266044 +/- 0.0002706817

lmY: 0.003266077 +/- 0.0002706865

Arima: 0.0033 4e-04 9.0497 0

@@

lmD: 0.001714761 +/- 0.0002777697

lmY: 0.001714817 +/- 0.0002777745

Arima: 0.0019 5e-04 4.0604 0

@@

lmD: 0.001677019 +/- 0.0003136298

lmY: 0.001677082 +/- 0.0003136353

Arima: 0.0018 5e-04 3.615 3e-04

@@

lmD: 0.9770065 +/- 0.1439346

lmY: 0.9770288 +/- 0.1439371

Arima: 1.041 0.2186 4.7611 0

@@

lmD: 0.8175029 +/- 0.1034317

lmY: 0.8175138 +/- 0.1034336

Arima: 0.8175 0.12 6.8102 0

@@

lmD: 0.216071 +/- 0.03807207

lmY: 0.2160751 +/- 0.03807275

Arima: 0.2161 0.0414 5.2169 0

@@

lmD: 0.190931 +/- 0.03787542

lmY: 0.1909357 +/- 0.03787609

Arima: 0.1909 0.0401 4.7631 0

@@

lmD: 0.4856759 +/- 0.04638817

lmY: 0.4856822 +/- 0.046389

Arima: 0.4857 0.0552 8.802 0

@@

lmD: 1.467857 +/- 0.1526559

lmY: 1.46788 +/- 0.1526586

Arima: 1.4679 0.1843 7.9642 0

@@

lmD: 0.00133588 +/- 0.0001367161

lmY: 0.001335895 +/- 0.0001367186

Arima: 0.0013 2e-04 8.5089 0

@@

lmD: 0.0004227125 +/- 5.903165e-05

lmY: 0.0004227187 +/- 5.90327e-05

Arima: 4e-04 1e-04 6.2905 0

@@

lmD: 0.0003723972 +/- 6.132751e-05

lmY: 0.0003724038 +/- 6.13286e-05

Arima: 4e-04 1e-04 5.4462 0

@@

lmD: 0.03656091 +/- 0.003621574

lmY: 0.03656153 +/- 0.003621638

Arima: 0.0366 0.0042 8.6966 0

@@

lmD: 0.1872084 +/- 0.2494764

lmY: 0.1872455 +/- 0.2494804

Arima: 0.1718 0.3646 0.4711 0.6376

@@

lmD: 0.04977389 +/- 0.1925048

lmY: 0.04979834 +/- 0.1925079

Arima: 0.0085 0.3464 0.0247 0.9803

@@

lmD: 0.0912485 +/- 0.1914527

lmY: 0.09127162 +/- 0.1914558

Arima: 0.05 0.3354 0.149 0.8816

@@

lmD: 0.03034705 +/- 0.02124537

lmY: 0.03034902 +/- 0.02124571

Arima: 0.0304 0.022 1.3788 0.1679

@@

lmD: 0.368357 +/- 0.2534977

lmY: 0.3683834 +/- 0.2535018

Arima: 0.3684 0.2583 1.4266 0.1537

@@

lmD: 0.0005084984 +/- 0.0002811406

lmY: 0.0005085061 +/- 0.0002811451

Arima: 5e-04 3e-04 1.5978 0.1101

@@

lmD: 0.000356478 +/- 0.0002141255

lmY: 0.0003564771 +/- 0.0002141289

Arima: 3e-04 3e-04 1.3203 0.1867

@@

lmD: 0.0003987357 +/- 0.0002210796

lmY: 0.0003987361 +/- 0.0002210831

Arima: 4e-04 3e-04 1.4505 0.1469

@@

lmD: 0.008776338 +/- 0.005506711

lmY: 0.00877684 +/- 0.005506799

Arima: 0.0088 0.0057 1.5378 0.1241

@@

@@

@@

\begin{verbatim}
2024-03-14 09:06:31.8 athan@tyler GHI_enh_04_investigate.R 1.124109 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-15}

@@

lmD: 1.566006 +/- 0.108321

lmY: 1.566022 +/- 0.108322

Arima: 1.566405 +/- 0.146687

@@

lmD: 0.950804 +/- 0.155249

lmY: 0.950827 +/- 0.155251

Arima: 1.022268 +/- 0.236917

@@

lmD: 1.086985 +/- 0.167871

lmY: 1.087013 +/- 0.167874

Arima: 1.159971 +/- 0.251086

@@

lmD: -0.012345 +/- 0.138879

lmY: -0.01233 +/- 0.138882

@@

Arima: -0.013183 +/- 6.904159

@@

Arima: 33.721354 +/- 8.881459

@@

lmD: 0.003266 +/- 0.000271

lmY: 0.003266 +/- 0.000271

Arima: 0.003291 +/- 0.000364

@@

lmD: 0.001715 +/- 0.000278

lmY: 0.001715 +/- 0.000278

Arima: 0.001886 +/- 0.000465

@@

lmD: 0.001677 +/- 0.000314

lmY: 0.001677 +/- 0.000314

Arima: 0.001849 +/- 0.000512

@@

lmD: 0.977006 +/- 0.143935

lmY: 0.977029 +/- 0.143937

Arima: 1.040956 +/- 0.218636

@@

lmD: 0.817503 +/- 0.103432

lmY: 0.817514 +/- 0.103434

Arima: 0.817505 +/- 0.120041

@@

lmD: 0.216071 +/- 0.038072

lmY: 0.216075 +/- 0.038073

Arima: 0.216075 +/- 0.041418

@@

lmD: 0.190931 +/- 0.037875

lmY: 0.190936 +/- 0.037876

Arima: 0.190936 +/- 0.040087

@@

lmD: 0.485676 +/- 0.046388

lmY: 0.485682 +/- 0.046389

Arima: 0.485682 +/- 0.055179

@@

lmD: 1.467857 +/- 0.152656

lmY: 1.46788 +/- 0.152659

Arima: 1.467877 +/- 0.18431

@@

lmD: 0.001336 +/- 0.000137

lmY: 0.001336 +/- 0.000137

Arima: 0.001336 +/- 0.000157

@@

lmD: 0.000423 +/- 5.9e-05

lmY: 0.000423 +/- 5.9e-05

Arima: 0.000423 +/- 6.7e-05

@@

lmD: 0.000372 +/- 6.1e-05

lmY: 0.000372 +/- 6.1e-05

Arima: 0.000372 +/- 6.8e-05

@@

lmD: 0.036561 +/- 0.003622

lmY: 0.036562 +/- 0.003622

Arima: 0.036562 +/- 0.004204

@@

lmD: 0.187208 +/- 0.249476

lmY: 0.187246 +/- 0.24948

Arima: 0.171775 +/- 0.364628

@@

lmD: 0.049774 +/- 0.192505

lmY: 0.049798 +/- 0.192508

Arima: 0.008548 +/- 0.346363

@@

lmD: 0.091248 +/- 0.191453

lmY: 0.091272 +/- 0.191456

Arima: 0.049975 +/- 0.33542

@@

lmD: 0.030347 +/- 0.021245

lmY: 0.030349 +/- 0.021246

Arima: 0.030378 +/- 0.022031

@@

lmD: 0.368357 +/- 0.253498

lmY: 0.368383 +/- 0.253502

Arima: 0.36844 +/- 0.258271

@@

lmD: 0.000508 +/- 0.000281

lmY: 0.000509 +/- 0.000281

Arima: 0.000508 +/- 0.000318

@@

lmD: 0.000356 +/- 0.000214

lmY: 0.000356 +/- 0.000214

Arima: 0.000349 +/- 0.000265

@@

lmD: 0.000399 +/- 0.000221

lmY: 0.000399 +/- 0.000221

Arima: 0.000392 +/- 0.00027

@@

lmD: 0.008776 +/- 0.005507

lmY: 0.008777 +/- 0.005507

Arima: 0.008799 +/- 0.005722

@@

Arima: 0.216075 +/- 0.041418

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_daily_trend-1} \end{center}

@@

Arima: 354.314467 +/- 35.576408

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-1} \end{center}

Arima: 127.193673 +/- 11.405953

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-2} \end{center}

@@

\begin{verbatim}
2024-03-15 10:49:24.4 athan@tyler GHI_enh_04_investigate.R 1.189463 mins
\end{verbatim}

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 13:12

```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
dailytrends <- data.table(
  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
dailytrends[DATA == "ST_E_daily"]

@@

@@

```{r CEmeanDaily, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
knitr::include_graphics("../images/daily-12.png")
```

>>>>

## Trends

```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
dailytrends <- data.table(
  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
dailyCE <- dailytrends[DATA == "ST_E_daily"]

@@

We have computed the daily trend of the mean over irradiance of CE (Figure\ \ref{fig:CEmeanDaily}), using

.... cite arima lag ....

```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."}
knitr::include_graphics("../images/P_daily_trend-1.png")
```

We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate],3)`\pm
`r round(dailyCE[var == "GLB_diff.mean", Tmod_Std..Error],3)`\,W/m^2$
on the mean over irradiance.

@@

<!-- ```{r CEmeanDaily2, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"} -->
<!-- knitr::include_graphics("../images/daily-12.png") -->
<!-- ``` -->
